A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-02-19 analysis/paper/paper.Rmd
fix label names in plots

```{r sample-size}
# number of each phase
library(tidyverse)
pre_E <- burial_three_period_age_number %>% filter(Phase == "pre") %>% pull()
post_E <- burial_three_period_age_number %>% filter(Phase == "post") %>% pull()
chi <- burial_three_period_age_number %>% filter(Phase == "chi") %>% pull()
disturb <- burial_three_period_age_number %>% filter(Phase == "disturbed") %>% pull()
diff_pre_post <- post_E - pre_E
```

@@

library(flextable)
# add column labels
ft <- flextable(posterior_esti_two_phases) %>% 
  set_header_labels(mean_pre = "pre-European", median_pre = "pre-European", 
                    `2.5%_pre` = "pre-European", `97.5%_pre` = "pre-European",
                    mean_post = "post-European", median_post = "post-European", 
                    `2.5%_post` = "post-European", `97.5%_post` = "post-European") %>%
  merge_at(i = 1, j = 2:5, part = "header") %>% 
  merge_at(i = 1, j = 6:9, part = "header") %>% 
  add_header_row(values = c("", "mean", "median", "2.5%", "97.5%",
                            "mean", "median", "2.5%", "97.5%"), top = FALSE ) %>% 
  align(j = 2:9, align = "right", part = "header") %>% 
  align(i = 1, align = "center", part = "header") %>% 
  width(j = ~ parameter, width = 1.3) %>% 
  width(j = 2:9, width = 0.65) %>% 
  set_caption("Estimated posterior means, medians, and 95% confidence intervals for each network parameter of two models. Confidence intervals that do not include zero indicate significant effects of parameters (Caimo, 2017). Posterior means are generally close to posterior medians.")
ft
```

@@

<!--archaeological implication based on the results-->
Network covariates give insights into the socio-cultural factors that were associated with the acquisition and distribution of foreign prestige goods. Our results indicate that the major factor contributing to burial networks is ritual for the pre-European network, and wealth for the post-European network. We interpret these results as illustrating different social and economic mechanisms influencing relations between burials for the two periods. Before European arrival, ritual behaviors were important factors that structured the interconnections of prestige goods in the burial contexts. This might imply that ritual could be a status indicator at the time before foreign goods were first introduced to Indigenous societies. After the European presence was established, status indicators shifted from ritual to wealth differences. Moreover, geographical proximity, implying some kinship association, has not effect on sharing similar prestige items between burials for both phases. This may suggest that the use of prestige items is more individual-oriented instead of kinship-based. Demographic information, such as age and sex, do not have any effects on network formation for both networks. But we also note that no effects could be due to the unavailability of age and sex values for many burials in our sample.

>>>>

```{r sample-size}
# number of each phase
library(tidyverse)
pre_E <- burial_three_period_age_number %>% filter(Phase == "pre") %>% pull()
post_E <- burial_three_period_age_number %>% filter(Phase == "post") %>% pull()
chi <- burial_three_period_age_number %>% filter(Phase == "chi") %>% pull()
disturb <- burial_three_period_age_number %>% filter(Phase == "disturbed") %>% pull()
diff_pre_post <- post_E - pre_E

# missing values
age_miss <- sum(NAs_age$n)
sex_miss <- sum(NAs_sex$n)
```

@@

library(flextable)
# add column labels
ft <- flextable(posterior_esti_two_phases) %>% 
  colformat_double(digits = 2) %>% 
  set_header_labels(mean_pre = "pre-European", median_pre = "pre-European", 
                    `2.5%_pre` = "pre-European", `97.5%_pre` = "pre-European",
                    mean_post = "post-European", median_post = "post-European", 
                    `2.5%_post` = "post-European", `97.5%_post` = "post-European") %>%
  merge_at(i = 1, j = 2:5, part = "header") %>% 
  merge_at(i = 1, j = 6:9, part = "header") %>% 
  add_header_row(values = c("", "mean", "median", "2.5%", "97.5%",
                            "mean", "median", "2.5%", "97.5%"), top = FALSE ) %>% 
  align(j = 2:9, align = "right", part = "header") %>% 
  align(i = 1, align = "center", part = "header") %>% 
  width(j = ~ parameter, width = 1.35) %>% 
  width(j = 2:9, width = 0.65) %>% 
  set_caption("Estimated posterior means, medians, and 95% confidence intervals for each network parameter of two models. Confidence intervals that do not include zero indicate significant effects of parameters (Caimo, 2017). Posterior means are generally close to posterior medians.")
ft
```

@@

<!--archaeological implication based on the results-->
Network covariates give insights into the socio-cultural factors that were associated with the acquisition and distribution of foreign prestige goods. Our results indicate that the major factor contributing to burial networks is ritual for the pre-European network, and wealth for the post-European network. We interpret these results as illustrating different social and economic mechanisms influencing relations between burials for the two periods. Before European arrival, ritual behaviors were important factors that structured the interconnections of prestige goods in the burial contexts. This might imply that ritual could be a status indicator at the time before foreign goods were first introduced to Indigenous societies. After the European presence was established, status indicators shifted from ritual to wealth differences. Moreover, geographical proximity, implying some kinship association, has not effect on sharing similar prestige items between burials for both phases. This may suggest that the use of prestige items is more individual-oriented instead of kinship-based. Demographic information, such as age and sex, do not have any effects on network formation for both networks. But we also note that no effects could be due to the unavailability of age and sex values for many burials (missing age = `r age_miss` and missing sex = `r sex_miss`) in our sample.
